Concurrent Programming with CXL

### 2020-06-29 book/paper.tex
Latest

\begin{figure}
\begin{code}
\begin{verbatim}
cxl -b -c NSLOTS=0 -c NPRODS=1 -c NCONSS=1 PCsema.cxl
cxl -b -c NSLOTS=1 -c NPRODS=0 -c NCONSS=1 PCsema.cxl
cxl    -c NSLOTS=1 -c NPRODS=1 -c NCONSS=0 PCsema.cxl
cxl    -c NSLOTS=1 -c NPRODS=1 -c NCONSS=1 PCsema.cxl
cxl -b -c NSLOTS=1 -c NPRODS=1 -c NCONSS=2 PCsema.cxl
cxl -b -c NSLOTS=1 -c NPRODS=2 -c NCONSS=0 PCsema.cxl
cxl    -c NSLOTS=1 -c NPRODS=2 -c NCONSS=1 PCsema.cxl
cxl    -c NSLOTS=1 -c NPRODS=2 -c NCONSS=2 PCsema.cxl
cxl -b -c NSLOTS=1 -c NPRODS=2 -c NCONSS=3 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=1 -c NCONSS=0 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=1 -c NCONSS=1 PCsema.cxl
cxl -b -c NSLOTS=2 -c NPRODS=1 -c NCONSS=2 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=2 -c NCONSS=0 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=2 -c NCONSS=1 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=2 -c NCONSS=2 PCsema.cxl
cxl -b -c NSLOTS=2 -c NPRODS=2 -c NCONSS=3 PCsema.cxl
cxl -b -c NSLOTS=2 -c NPRODS=3 -c NCONSS=0 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=3 -c NCONSS=1 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=3 -c NCONSS=2 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=3 -c NCONSS=3 PCsema.cxl
\end{verbatim}
\end{code}
\caption{Script for testing producer/consumer synchronization
(assuming the code is in file \texttt{PCsema.cxl}).}
\label{fig:pcscript}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{BBsemadata}
\end{code}
\caption{[BBsemadata.cxl] Test whether the bounded buffer delivers the right data in the
right order.}
\label{fig:PCsemadata}
\end{figure}

@@

Figure~\ref{fig:PCsemadata} tests whether the correct data is sent in
the correct order.  There are the same number of producers and consumers.
Each producer $i$ produces two tuples: $(i, 0)$ and $(i, 1)$ in that order.
Each consumer consumes two tuples and checks that the tuples are different
and that, if the two tuples come from the same producer, then they have to
be in the order sent.
Moreover, consumers add the tuples they received to the set
\texttt{received} (atomically---a lock could have been used here as well).)
The \texttt{main()} process waits for all consumers to have received
exactly the set of tuples that the producers produce.

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
name tag & a dictionary with atoms \texttt{.name} and \texttt{.tag} \\
\hline
program counter & an integer value pointing into the code \\
\hline
frame pointer & an integer value pointing into the stack \\
\hline
atomic & if non-zero, the process is in atomic mode \\
\hline
stack & a list of CXL values \\
\hline
register & a CXL dictionary mapping atoms (representing process variables) to CXL values \\
\hline
stopped & a boolean indicating if the context is stopped \\
\hline
\end{tabular}
\vspace{1em}

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
code & a list of CVM machine instructions \\
\hline
labels & a dictionary of atoms to program counters \\
\hline
variables & a dictionnary mapping atoms to values \\
\hline
ctxbag & a bag of non-stopped contexts \\
\hline
stopbag & a bag of stopped contexts \\
\hline
choosing & if not \texttt{None}, indicates a context that is choosing \\
\hline
failure & boolean indicating some context has failed \\
\hline
initializing & boolean indicating that the state is not fully initialized. \\
\hline
\end{tabular}
\vspace{1em}

>>>>

\begin{figure}
\begin{code}
\begin{verbatim}
cxl -b -c NSLOTS=0 -c NPRODS=1 -c NCONSS=1 BBsematest.cxl
cxl -b -c NSLOTS=1 -c NPRODS=0 -c NCONSS=1 BBsematest.cxl
cxl    -c NSLOTS=1 -c NPRODS=1 -c NCONSS=0 BBsematest.cxl
cxl    -c NSLOTS=1 -c NPRODS=1 -c NCONSS=1 BBsematest.cxl
cxl -b -c NSLOTS=1 -c NPRODS=1 -c NCONSS=2 BBsematest.cxl
cxl -b -c NSLOTS=1 -c NPRODS=2 -c NCONSS=0 BBsematest.cxl
cxl    -c NSLOTS=1 -c NPRODS=2 -c NCONSS=1 BBsematest.cxl
cxl    -c NSLOTS=1 -c NPRODS=2 -c NCONSS=2 BBsematest.cxl
cxl -b -c NSLOTS=1 -c NPRODS=2 -c NCONSS=3 BBsematest.cxl
cxl    -c NSLOTS=2 -c NPRODS=1 -c NCONSS=0 BBsematest.cxl
cxl    -c NSLOTS=2 -c NPRODS=1 -c NCONSS=1 BBsematest.cxl
cxl -b -c NSLOTS=2 -c NPRODS=1 -c NCONSS=2 BBsematest.cxl
cxl    -c NSLOTS=2 -c NPRODS=2 -c NCONSS=0 BBsematest.cxl
cxl    -c NSLOTS=2 -c NPRODS=2 -c NCONSS=1 BBsematest.cxl
cxl    -c NSLOTS=2 -c NPRODS=2 -c NCONSS=2 BBsematest.cxl
cxl -b -c NSLOTS=2 -c NPRODS=2 -c NCONSS=3 BBsematest.cxl
cxl -b -c NSLOTS=2 -c NPRODS=3 -c NCONSS=0 BBsematest.cxl
cxl    -c NSLOTS=2 -c NPRODS=3 -c NCONSS=1 BBsematest.cxl
cxl    -c NSLOTS=2 -c NPRODS=3 -c NCONSS=2 BBsematest.cxl
cxl    -c NSLOTS=2 -c NPRODS=3 -c NCONSS=3 BBsematest.cxl
\end{verbatim}
\end{code}
\caption{Script for testing producer/consumer synchronization
(assuming the code is in file \texttt{BBsematest.cxl}).}
\label{fig:pcscript}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{BBsemadata}
\end{code}
\caption{[BBsemadata.cxl] Test whether the bounded buffer delivers the right data in the
right order.}
\label{fig:BBsemadata}
\end{figure}

@@

Figure~\ref{fig:BBsemadata} tests whether the correct data is sent in
the correct order.  There are the same number of producers and consumers.
Each producer $i$ produces two tuples: $(i, 0)$ and $(i, 1)$ in that order.
Each consumer consumes two tuples and checks that the tuples are different
and that, if the two tuples come from the same producer, then they have to
be in the order sent.
Moreover, consumers add the tuples they received to the set
\texttt{received} (atomically---a lock could have been used here as well).)
The \texttt{main()} process waits for all consumers to have received
exactly the set of tuples that the producers produce.

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
name tag & a dictionary with atoms \texttt{.name} and \texttt{.tag} \\
\hline
program counter & an integer value pointing into the code \\
\hline
frame pointer & an integer value pointing into the stack \\
\hline
atomic & if non-zero, the process is in atomic mode \\
\hline
stack & a list of CXL values \\
\hline
register & a CXL dictionary mapping atoms (representing process variables) to CXL values \\
\hline
stopped & a boolean indicating if the context is stopped \\
\hline
failure & if not None, string that describes how the process failed \\
\hline
\end{tabular}
\vspace{1em}

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
code & a list of CVM machine instructions \\
\hline
labels & a dictionary of atoms to program counters \\
\hline
variables & a dictionnary mapping atoms to values \\
\hline
ctxbag & a bag of non-stopped contexts \\
\hline
stopbag & a bag of stopped contexts \\
\hline
choosing & if not \texttt{None}, indicates a context that is choosing \\
\hline
initializing & boolean indicating that the state is not fully initialized. \\
\hline
\end{tabular}
\vspace{1em}
